---
title: The distribution of article co-authorship for a small sample of Moroccan journals
  (N=23) in 2019.
author: "Oumnia Chellah"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
  rmarkdown::pdf_document:
    fig_caption: yes
    includes:
      in_header: my_header.tex
  pdf_document: default
---

```{r setup, include=FALSE}
# knitr options
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

The map below shows the links among 111 co-authors involved in publishing 34 articles from a sample of 23 Moroccan journals published in 2019, with each dot representing the city with the university at which one or more co-authors work. The extent of co-authorship will be re-examined some years after the journal platform is upgraded and indexing improved to see if this leads to greater collaboration among researchers within Morocco and beyond. 

```{r}

library(plotly)
library(dplyr)


# airport locations
journals <- read.csv("data/oumnia_map copy.csv")
# flights between airports
connections <- read.csv("data/connections.csv")
connections$id <- seq_len(nrow(connections))

# map projection
geo_two <- list(
  scope = 'africa',
  projection = list(type = 'azimuthal equal area'),
  showland = TRUE,
  landcolor = toRGB("gray95"),
  countrycolor = toRGB("gray80")
)

fig_2 <- plot_geo(locationmode = 'Morocco', color = I("red"))
fig_2 <- fig_2 %>% add_markers(
  data = journals, x = ~lon, y = ~lat, text = ~paste(city, "\n", "Co-authors:", authors, "\n", "Articles:", articles),
  size = 25000, hoverinfo = "text", alpha = 0.5
)

fig_2 <- fig_2 %>% add_segments(
    data = group_by(connections, id),
    x = ~lon_start, xend = ~lon_end,
    y = ~lat_start, yend = ~lat_end,
    text = ~journal,
    alpha = 0.3, hoverinfo = "none"
  )

fig_2 <- fig_2 %>% style(
    hoveron= "fill"
)


#Sets title and legend
fig_2 <- fig_2 %>% layout(
    geo = geo_two, showlegend = FALSE
  )
fig_2
```

Below is a list of the journals containing the articles used for the co-authorship links:

```{r}
journal_list <- read.csv(file = 'data/Journal Names.csv')
journal_list
```

